### 2016-01-18 papers/CAFe/HIPS-paper/conclusions.tex
Fixed last remaining references.

However, significant challenges arise as hardware adapts to the end of Moore's
Law\cite{exascale:workshop:2011}.  The revolution occurring in hardware architecture
has completely altered the landscape for scientific computing as a code designed for the
distributed memory bulk synchronous model of parallelism may actually run slower on
advanced hardware\cite{Dubey:2014:SSC:2686745.2686756}.

Parallelism was added to Fortran with the addition of coarrays in the 2008
standard\cite{fortran:2008} to enable the migration of codes as hardware evolves.
Significant language features were left out of this early version of coarrays as
identified by \emph{Mellor-Crummy et al}\cite{mellor-crummey:2009:caf2}.  Many of these features
have been adopted in what is likely to be called the 2015 standard of the language\cite{fortran:2015},
such as teams of program images and improved synchronization constructs like events.

>>>>

However, significant challenges arise as hardware adapts to the end of Moore's
Law\cite{ashby2010opportunities}.  The revolution occurring in hardware architecture
has completely altered the landscape for scientific computing as a code designed for the
distributed memory bulk synchronous model of parallelism may actually run slower on
advanced hardware\cite{Dubey:2014:SSC:2686745.2686756}.

Parallelism was added to Fortran with the addition of coarrays in the 2008
standard\cite{Reid:2008:NFF:1408643.1408645} to enable the migration of codes as hardware evolves.
Significant language features were left out of this early version of coarrays as
identified by \emph{Mellor-Crummy et al}\cite{mellor-crummey:2009:caf2}.  Many of these features
have been adopted in what is likely to be called the 2015 standard of the language\cite{fortran:2015},
such as teams of program images and improved synchronization constructs like events.
